### 2023-04-03 reachable-resilience.tex
up
only one tabular now

\mathieu{I moved the proof to the appendix since it's a slight adjustment but takes a lot of room.}

Since reachability of $0$ is undecidable in Reset Petri-Nets, the reduction implies the following:

@@

\subsection{Other}

\mathieu{Should try to put all results in a single table}

@@

>>>>

% \mathieu{I moved the proof to the appendix since it's a slight adjustment but takes a lot of room.}
\begin{proof}
See Appendix~\ref{appendix} for the complete proof.
\end{proof}

Since the Reset Petri Net zero reachability problem is undecidable in Reset Petri-Nets, the reduction implies the following:

@@

\subsection{Synthesis}

\iffalse
\mathieu{Should try to put all results in a single table}

@@

Results in the case $\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$:

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong compatibility ~ & $\uparrow post^*$ effective & both  \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Corollary~\ref{bsrp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Corollary~\ref{bsrp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}
